How Kids Code and How We Know:\\An Exploratory Study on the Scratch Repository

### 2016-06-14 Paper/paper.tex
Removed deep understanding, clarified that only product data is used

The goal of this paper is to obtain a deep understanding of how people program in Scratch, to analyze the characteristics of Scratch programs, and to quantitatively evaluate the use of programming abstractions and concepts. Moreover, knowing that bad programming habits and code smells can be harmful \cite{hermans_2016}, we also want to explore whether they are common. To address this goal, we answer the following research questions:

>>>>

The goal of this paper is to obtain an understanding of how people program in Scratch by analyzing their programming artifacts, i.e., the saved and shared Scratch projects, and to quantitatively evaluate the use of programming abstractions and concepts. Moreover, knowing that bad programming habits and code smells can be harmful \cite{hermans_2016}, we also want to explore whether they are common. To address this goal, we answer the following research questions:
